
\documentclass[11pt]{article}


\usepackage{amsmath,amsthm,amssymb}
\usepackage[margin=1.5in]{geometry}

\newtheorem*{thm}{Theorem}
\newtheorem*{cnj}{Conjecture}
\newtheorem*{lem}{Lemma}
\newtheorem*{cor}{Corollary}
\newtheorem*{prop}{Proposition}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}

\usepackage{hyperref}

\title{Mid Semester Reflection}
\author{Your Name Here}
\date{April 6, 2020 (due)}

\begin{document}



\maketitle

\begin{enumerate}

\item {\bf Of the proofs in the proof portfolio thus far, of which proof are you the most proud? Which proof in this proof portfolio has been the biggest challenge for you thus far?}
\vspace{.1in}

%Put your response here. This is your response to the first reflection question.

\vspace{.3in}




\item {\bf What insights (``Aha!" moments) have you had about the process of proving results and writing up proofs for your proof portfolio or throughout this course?}
\vspace{.1in}

%Put your response here. This is your response to the second reflection question.

\vspace{.3in}




\item {\bf Watch the following  short videos: 
	\begin{itemize}
	\item John Legend on Success: \url{http://bit.ly/2Xm2hbK},  
	\item Michael Starbird on Making Mistakes:  \url{http://bit.ly/2tC1BBh}. 
	\end{itemize}
Identify one time you have made a mistake in MTH 210. What was your attitude toward making that mistake? In the last video the speaker refers to ``the right attitude towards making mistakes". What do you think the ideal attitude towards making mistakes should be?}
\vspace{.1in}

%Put your response here. This is your response to the third reflection question.

\vspace{.3in}

\item {\bf What is one skill you feel you have developed in MTH 210 so far? What is one goal you have for yourself concerning MTH 210?  (It could be related to the proof portfolio, could be a skill you want to develop, or a study habit you want to have.)}
\vspace{.1in}

%Put your response here. %This is your response to the fourth reflection question.

\vspace{.3in}

\item {\bf Finally, if math were an animal, what animal would it be and why?}

%Put your response here. %This is your response to the fifth reflection question.

\end{enumerate}

\end{document}