\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{nopageno}
\usepackage{hyperref}
\usepackage{multicol}


\usepackage{amsmath,amssymb,graphicx}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\cM}{\mathcal{M}}
\usepackage{xcolor}
\newcommand{\blue}{\textcolor{blue}}

\usepackage{versions}
\excludeversion{solution}

\newcommand{\bs}{\begin{solution}}
\newcommand{\es}{\end{solution}}



\begin{document}
\vspace{-1.2in}
\begin{center} \textbf{\Large{Skill Mastery Quiz 5}} \\
Communicating in Math (MTH 210-01)\\
Winter 2020
\end{center}



\noindent Name: 




\begin{itemize}
	

\item[L5-3] Write a useful negation of the following statement:
		\begin{center}
For all integers $n$ and $m$, if $nm$ is even then $n$ is even or $m$ is even.		\end{center}
		Useful negations don't start with ``It is not true that..." and avoid the word not in cases where it could be replaced (e.g., don't use ``not even").

\bs \textcolor{blue}{A negation is: ``there exist integers $n$ and $m$ such that $nm$ is even and $n$ is odd and $m$ is odd."}
\end{solution}

\vfill

\item[P3-1]  The following statement is incorrect:
		\begin{center}
The set of natural numbers is closed under subtraction.		
	\end{center}
			Show the statement is false using a counterexample. You should clearly explain why the counterexample you found shows the statement is false.


\bs \textcolor{blue}{This statement is false and there are many counterexamples. Saying the set $\N$ is closed under subtraction means that for any $a,b\in\N$ we have $a-b\in N$. For one counterexample, consider $a=1$ and $b=5$. Then $a-b = 1-5 = -4$ and $-4$ is not a natural number.}\end{solution}
\vfill

\newpage

\item[P1-1] Consider the following statement:
		\begin{center}
		If $n$ is even integer greater than $2$ then $n$ can be expressed as the sum of two prime numbers.
		\end{center}
	State what you would assume in a direct proof. 
	
	\bs\textcolor{blue}{Assume that $n$ is an even integer greater than $2$.}\end{solution}
	
	\vfill
	
	
	State what you would assume in a proof by contradiction.
	
	\bs\textcolor{blue}{Assume that $n$ is an even integer greater than $2$ and that $n$ can not be expressed as the sum of two prime numbers.}\end{solution}
\vfill

\end{itemize}
	

\end{document}
